\documentclass[oneside]{book}

%standalone class ?? http://www.ctan.org/pkg/standalone

\usepackage{amsmath,amsthm}
\usepackage{hyperref}
%\usepackage{graphicx}
%\usepackage{url}
\usepackage{amsfonts}
%\usepackage{multicol}
\usepackage{geometry}
\usepackage[table,xcdraw]{xcolor}

%\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{claim}[theorem]{Claim}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem*{proposition}[Theorem]{Proposition}
\newtheorem*{proposition}{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{observation}{Observation}
\newtheorem*{example}{Example}
\newtheorem*{remark}{Remark}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}

\allowdisplaybreaks

\setcounter{secnumdepth}{1} % levels under \section are not numbered

\begin{document}

    \title{Exercises Apostol 2}

    \author{Nilo de Roock}

    \maketitle

    \input{chapters/chp00.tex}

    \tableofcontents

    \chapter{Elliptic Functions}
%    \input{chapters/chp01-1Def.tex}
%    \input{chapters/chp01-2Thm.tex}
    \input{chapters/chp01-3Exc.tex}

    \chapter{The modular group and modular functions}
    \input{chapters/chp02-1Def.tex}
    \input{chapters/chp02-2Thm.tex}
    \input{chapters/chp02-3Exc.tex}


    \begin{thebibliography}{3}

        \bibitem{example1}
        Leader, S. (1986). What is a differential? A new answer from teh generalized Riemann integral. {\it Amer. Math. Monthly.\/} 93(5): 348--356.

        \bibitem{example2}
        Steeb, W.-H. (1996). \textit{Continuous Symmetries, Lie Algebras, Differential Equations and Computer Algebra.\/} River Edge, NJ: World Scientific Publishing.  \href{http://dx.doi.org/10.1142/3309}{\url{http://dx.doi.org/10.1142/3309}}

        \bibitem{example3}
        Titchmarsh, E. C. (1986). {\it The Theory of the Riemann Zeta-Function.\/} 2nd. ed. Edited and with a preface by D. R. Heath-Brown. New York: The Clarendon Press, Oxford Univ. Press.

    \end{thebibliography}

\end{document}
